---
title: "Plotly"
output:
  html_document:
    toc: true
    toc_float: true
---

## Loading data
We're gonna look at Instacart data:

```{r message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r warning = FALSE}
data("instacart")

instacart = 
  instacart %>% 
  as_tibble(instacart) %>% 
  select(order_hour_of_day, aisle, department) %>% 
  filter(department %in% c("produce","dairy eggs"))
```


## Plotly plots
### Barchart
This is a barchart that shows the number of items ordered in each aisle from _Produce_ or _Dairy/Eggs_ departments (aisles are ordered by ascending number of items).
```{r warning = FALSE}
  instacart %>% 
  count(aisle, department) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  plot_ly(x = ~aisle, y = ~n, color = ~department, type = "bar", colors = "viridis") %>% 
  layout(title  = "Number of items ordered in each aisle of Produce or Dairy/Eggs", 
         xaxis = list(title = "Aisle"), yaxis = list(title = "Number of items ordered"))
```

### Boxplot
This is a barchart that shows the distribution of order time in hours for each aisle from _Produce_ or _Dairy/Eggs_ departments (aisles are ordered by ascending median order time).
```{r}
instacart %>% 
  mutate(aisle = fct_reorder(aisle, order_hour_of_day)) %>% 
  plot_ly(x = ~aisle, y = ~order_hour_of_day, color = ~department, type = "box", colors = "viridis") %>% 
  layout(title  = "Order time in hours for each aisle of Produce or Dairy/Eggs", 
         xaxis = list(title = "Aisle"), yaxis = list(title = "Order time in hours"))
```

### Line plot
This is a line plot that shows the distribution of the number of items ordered over hours of day, for each aisle from _Produce_ or _Dairy/Eggs_ departments.
```{r}
instacart %>% 
  count(aisle, order_hour_of_day) %>% 
  plot_ly(x = ~order_hour_of_day, y = ~n, color = ~aisle, type = "scatter", mode = "line", colors = "viridis") %>% 
  layout(title  = "Number of items ordered over hours of day for each aisle", xaxis = list(title = "Order time in hours"), yaxis = list(title = "Number of items ordered"))
```

